### 2021-08-26 plos_latex_template.tex
ast - some changes in rule 1. the don'ts.

Diversity encompasses multiple dimensions: age, physical ability, career stage, gender, gender identity,  geographic origin, language, neurodiversity, race, religion, sexual orientation, and socioeconomic background, to name a few. Human diversity should be celebrated and respected in every way. Nonetheless, there are implicit hierarchies along these axes, and some statuses (e.g., cisgender, white, male, from the US or Europe) hold the privilege of being the default settings for which all systems --including conferences-- are consciously and unconsciously built. As a result, most people in the world fall into some category where they are part of a marginalized group --as opposed to a privileged one. A more diverse and inclusive conference  starts by recognizing that people are diverse, and that some groups face discrimination (some more than others) and might be underrepresented in your community and event \cite{timperleyHeMoanaPukepuke2020} because of these implicit hierarchies.

Think about the reasons why you want to create a more diverse conference. This may be important to you, whether you come from a privileged background or not. Along this paper, Do not treat diversity as a checklist, do not use people from minoritized groups for image purposes, and do not act as a benefactor or savior but as a genuine collaborator.

%Thinking about diversity and inclusion is thinking about counteracting the structures that hold these hierarchies in place.

@@

While it is essential to improve representation towards some of the most visible dimensions of human diversity, such as race, gender, and country of origin, building a truly inclusive environment means taking care of all the other aspects of diversity as well. Having consideration of religious practices, setting specific accommodations for lactating women and child care, having LGBTIQ+-friendly spaces, creating community-only spaces, enforcing the use of pronouns, and treating gender as a non-binary variable are just some examples of decisions that can make inclusion real.

@@

The code of conduct team should receive training on how to receive reports, respond to incidents, and communicate their responses. A diverse code of conduct team will be more understanding of power dynamics, and sensitive to discrimination and harassment. We strongly recommend reading How to enforce a Code of Conduct by Valerie Aurora (\url{https://frameshiftconsulting.com/resources/code-of-conduct-book/}) as an excellent starting point for the Code of Conduct team work.

@@

Most advice when working with a diverse team should apply to every team, but is especially true when working with people from marginalized groups. First, delegate. Don't expect self-nomination and voting to work as mechanisms to counteract systemic inequalities. Nominate directly and offer coordinating positions, even if this means stepping down. Offer mentorship and guidance if you encounter cases of impostor syndrome, doubts about the use of English in communication \ref{rule_language}, or others. Break the expectations about leadership as a lonely task and create smaller, co-led groups, where everyone finds their preferred tasks and gets to take leadership. Splitting the workload and responsibilities should not be done by putting care-taking labors --community building, meeting organization and note taking, conversations with potential partners-- on the hands of women and other minoritized groups, while men take the lead in stereotypical highly-valued tasks (see Rule \ref{rule_spotlight}).

>>>>

Diversity encompasses multiple dimensions: age, physical ability, career stage, gender, gender identity,  geographic origin, language, neurodiversity, race, religion, sexual orientation, and socioeconomic background, to name a few. Human diversity should be celebrated and respected in every way. Nonetheless, there are implicit hierarchies along these axes, and some statuses (e.g., cisgender, white, male, from the US or Europe) hold the privilege of being the default settings for which all systems --including conferences-- are consciously and unconsciously built. While no isolated initiative can change reality by itself, building a more diverse and inclusive conference starts by recognizing that these inequalities have excluded systematically whole groups of people from academia and from scientific and professional circles \cite{timperleyHeMoanaPukepuke2020}.

Think about the reasons why you want to create a more diverse conference and try not to treat diversity as a checklist, avoid using diversity and inclusion work for image purposes, and do not act as a benefactor or savior but as a genuine collaborator.
%andrea: this is here because we want to avoid readers to read as recipes and treat this less seriously than how it should (and then blaming the recipe). i am not sure of the phrasing or position in the text."genuine collaborator" is in the spirit of co-liberation/co-conspirator

@@

While it is essential to improve representation towards some of the most visible dimensions of human diversity, such as race, gender, and country of origin, building a truly inclusive environment means taking care of all the other aspects of diversity as well. Having consideration of religious practices, setting specific accommodations for breastfeeding and child care, having LGBTIQ+-friendly spaces, creating community-only spaces, enforcing the use of pronouns, and treating gender as a non-binary variable are just some examples of decisions that can make inclusion real. Importantly, you can take active steps in creating a more welcoming environment without requiring anyone to disclose personal information.

@@

The code of conduct team should receive training on how to receive reports, respond to incidents, and communicate their responses. A diverse code of conduct team will be more understanding of power dynamics and sensitive to discrimination and harassment issues. We strongly recommend reading How to enforce a Code of Conduct by Valerie Aurora (\url{https://frameshiftconsulting.com/resources/code-of-conduct-book/}) as an excellent starting point for the Code of Conduct team work.

@@

Most advice when working with a diverse team should apply to every team, but is especially true when working with people from marginalized groups. First, delegate. Don't expect self-nomination and voting to work as mechanisms to counteract systemic inequalities. Nominate directly and offer coordinating positions, even if this means stepping down. Offer mentorship and guidance if you encounter cases of impostor syndrome, doubts about the use of English in communication (See Rule \ref{rule_language}), or others. Break the expectations about leadership as a lonely task and create smaller, co-led groups, where everyone finds their preferred tasks and gets to take leadership. Splitting the workload and responsibilities should not be done by putting care-taking labors --community building, meeting organization and note taking, conversations with potential partners-- on the hands of women and other minoritized groups, while men take the lead in stereotypical highly-valued tasks (see Rule \ref{rule_spotlight}).
